---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(pryr)
```

# daTrimmer

`daTrimmer` is a lightweight toolkit to trim a (potentially big) R object without
breaking the results of a given function call, where the (trimmed) R object
is given as argument.

The `trim` function is the bread and butter of `daTrimmer`. It seeks to reduce
the size of an R object by recursively removing elements from the object 
one-by-one. It does so in a 'greedy' fashion - it constantly tries to 
remove the element that uses the most memory. 

The trimming process is constrained by a reference function call. The trimming 
procedure will not allow elements to be removed from the object, that will 
cause results from the function call to diverge from the original results of 
the function call.

## Installation

`daTrimmer` can be installed with `install.packages('daTrimmer')`. 

## Workflow Example

Get ready by loading the package.

```{r}
library(daTrimmer)
```

Train a model on the famous `mtcars` data set. 

```{r}
# load training data.
trn <- datasets::mtcars

# estimate model.
mdl <- lm(mpg ~ ., data = trn)
```

I want to trim the model object `mdl` as possible without affecting the predictions,
computed with function `predict()`, for the resulting model. 

The trimming is then simply conducted by invoking: 

```{r}
mdl_trim <- trim(obj = mdl,
                 obj_arg_name = "object",
                 fun = predict,
                 newdata = trn)
```

And that's it!

Note, that I provide the `trim` function with the extra argument `newdata`, that
is passed to the function call with `fun`. This means, that the trimming is 
constrained by, that the results of 'fun' (=`predict`) _MUST_ be exactly the same
on these data before and after the trimming.

The trimmed model object now measures `r pf_obj_size(object_size(mdl_trim))`. The original 
object measured `r pf_obj_size(object_size(mdl))`.

For more information about how to use `daTrimmer`, please take a look at the
vignette:

```{r, eval = FALSE}
vignettes("daTrimmer")
```

Enjoy `daTrimmer`! :)
